Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-10-15 paper/post_tci.tex
minor changes

\subsection{Tuning of parameters}
\label{sec:tuning_parameters}
$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
need to be chosen carefully for optimal reconstruction. In our
experiments, $\lambda_1$ was tuned in such a way as to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, regions of interest (RoI) are obviously
not known in advance, and thus not considered for the purpose of
tuning.  Further, this value was retained for our spatially-varying
prior-based reconstruction as well, that is, the value optimized for
the TV-only regularize is maintained for the method proposed in this
paper.  In principle, one could have jointly optimized both
$\lambda_1$ and $\lambda_2$ to get even better results compared to the
one we have in Sections~\ref{sec:results_with_imaging_model},
and~\ref{sec:results_without_imaging_model}.  The value of $\lambda_2$
largely depends on the amount of artefacts one aims to remove by using
object-prior at the cost of their dominance in the new regions. This
value was empirically chosen to lie between $0--3$ for our datasets
(having the fixed $\lambda_1$).

The hyper-parameter $k$ defines the sensitivity of the weights map to
the difference between test image and object-prior (projection of test
onto the space of object-prior). When $k=0$, our method behaves
similar to the reconstruction using TV-only regularization. As $k$
increases, the weights map starts capturing new changes in the test,
at the cost of detecting a few false positives i.e., false new
changes. In other words, as the weights-map becomes more sensitive to
the difference between the test and object-prior, it becomes more
noisy. In order to visualize the effect of the hyper-parameter $k$, we
performed 2D reconstructions on okra dataset for different values of
$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
obtained for each of the $k$ values and
Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
final reconstructions. We run our experiments for a few values of $k$
and empirically choose the best reconstruction based on our tolerance
for noise in the weights-map.  However, when a large number of
templates are available, instead of this empirical method, this
parameter can be chosen by assuming one of the templates as a
pseudo-test and validating the $k$ that results in the best
reconstruction (also see Sec~3 of \cite{supp_paper}.

>>>>

\subsection{Tuning of parameters}
\label{sec:tuning_parameters}
$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
need to be chosen carefully for optimal reconstruction. In our
experiments, $\lambda_1$ was tuned in such a way as to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, regions of interest (RoI) are obviously
not known in advance, and thus not considered for the purpose of
tuning.  Further, this value was retained for our spatially-varying
prior-based reconstruction as well, that is, the value optimized for
the TV-only regularizer is maintained for the method proposed in this
paper.  In principle, one could have jointly optimized both
$\lambda_1$ and $\lambda_2$ to get even better results compared to the
one we have in Sections~\ref{sec:results_with_imaging_model},
and~\ref{sec:results_without_imaging_model}.  The value of $\lambda_2$
largely depends on the amount of artefacts one aims to remove by the
use of object-prior at the cost of their dominance in the new
regions. This value was empirically chosen to lie between $(0,3)$ for
our datasets (having the fixed $\lambda_1$).

The hyper-parameter $k$ defines the sensitivity of the weights map to
the difference between test image and object-prior (projection of test
onto the space of object-prior). When $k=0$, our method behaves
similar to the reconstruction using TV-only regularization. As $k$
increases, the weights map starts capturing new changes in the test,
at the cost of detecting a few false positives i.e., false new
changes. In other words, as the weights-map becomes more sensitive to
the difference between the test and object-prior, it becomes more
noisy. In order to visualize the effect of the hyper-parameter $k$, we
performed 2D reconstructions on okra dataset for different values of
$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
obtained for each of the $k$ values and
Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
final reconstructions. We run our experiments for a few values of $k$
and empirically choose the best reconstruction based on our tolerance
for noise in the weights-map.  However, when a large number of
templates are available, instead of this empirical method, this
parameter can be chosen by assuming one of the templates as a
pseudo-test and validating the $k$ that results in the best
reconstruction (also see Sec~3 of \cite{supp_paper}.
